DeepSphere: a graph-based spherical CNN

### 2019-09-24 main.tex
shortcut macros for S and R

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{siunitx} % used in SHREC table
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
\usepackage[export]{adjustbox} % figure vertical alignment
\usepackage{subfig}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\renewcommand{\b}[1]{{\bm{#1}}}   % bold symbol

@@

\renewcommand{\figref}[1]{figure~\ref{fig:#1}}
\renewcommand{\Figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\tabref}[1]{table~\ref{tab:#1}}
\newcommand{\Tabref}[1]{Table~\ref{tab:#1}}
\renewcommand{\secref}[1]{section~\ref{sec:#1}}
\renewcommand{\Secref}[1]{Section~\ref{sec:#1}}
%\newcommand{\secref}[1]{\S\ref{sec:#1}}
\newcommand{\eqnref}[1]{equation~(\ref{eqn:#1})}
\newcommand{\Eqnref}[1]{Equation~(\ref{eqn:#1})}

@@

\subsection{Problem formulation}
% The plan for this section
% 0.1 Explain the sampling problem
As the graph convolution acts on a sampled version of the function $\b{f}$ and the rotation on its continuous counterpart $f$, a sampling operator is needed.
Given a sampling scheme $V=\{x_i\in\mathbb S^2, i=0, \dots, n\}$ of the sphere and a function $f : \mathbb S^2 \supset F_V \to \mathbb R$, the sampling operator $T_V: L^2(\mathbb S^2) \supset F\to \mathbb R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(x_i)$, where $F_V$ suitable subspace of $L^2(\mathbb S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing (\cite{driscoll1994Fouriersphere}).
For most sampling schemes, it is not known if $F_V$ exist and hence if $T_V$ is invertible. A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds, and thus we have a closed form of $T_V^{-1}$ is known. % \cite{driscoll1994Fouriersphere}
For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\bf{f}$, thus approximating $T_V^{-1}$.
For all theoretical consideration, we assume that $F_V$ exists and $f \in F_V$.

@@

\paragraph{Theoretical convergence.}
We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme. 
Given a sampling scheme $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
\begin{theorem}
	For a sampling $V = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\mathbb S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\mathbb S^2}$  for $n\to\infty$:
	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hint for equivariance.
Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{sec: appendix: proof of theorem} inspires us in the construction of our graph Laplacian. It gives us a strong hint how the parameter $t$ needs to be adjusted with respect to the number of points $n$.

@@

\paragraph{Preliminaries.}
The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_Vf=\b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
The proof is constructed by leveraging 3 different operators:
\begin{itemize}
    \item The extended graph Laplacian operator is a functional $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
	Note that we have the following relation $\b{L}_n^t \b{f} = T_V L_n^t f$.
	\item The functional approximation to the Laplace-Beltrami operator is a functional $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
	\begin{equation}
    \label{eq:Functional approximation to the Laplace-Beltrami operator}
	L^tf(y) = \int_{\mathcal{M}} \exp^{-\frac{\|y-x\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
	\end{equation}
	where given $\mu$ be the uniform probability measure on the manifold $\mathcal{M}$, and let $\text{vol}(\mathcal{M})$ be the volume of $\mathcal{M}$.
	\item 
	The Laplace-Beltrami operator $\Delta_{\mathcal{M}}$ is defined as the divergence of the gradient
	\begin{equation}
        \label{eq:laplace-beltrami}
        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
    \end{equation}
    of a differentiable function $f: \mathcal M\rightarrow \mathbb R$. The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$

@@

% it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
% where $L_n^t$ is defined as follows:

@@

We start by proving the following Proposition:
\vspace{0.5cm}
\begin{prop}\label{prop:1}
	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $\mathcal L_f$
	$$
	\left| \int_{\mathbb S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.
	$$
	Furthermore, for all $y\in\mathbb S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
	$$ L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).$$
\end{prop}
\vspace{0.5cm}

@@

	Let us assume that the function $f:\mathbb R^3\rightarrow \mathbb R$ is Lipschitz with Lipschitz constant $\mathcal L_f$, we have

@@

	So, by triangular inequality and by summing all the contributions of all the $n$ patches
	$$\left| \int_{\mathbb S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  \mathcal L_fd^{(n)}\frac{1}{n} = \mathcal L_fd^{(n)}$$
	Thanks to this result, we have the following two pointwise convergences

	$$\forall f \text{ Lipschiz,}\quad \forall y\in\mathbb S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}\rightarrow \int e^{-\frac{||x-y||^2}{4t}}d\mu(x)$$
	$$\forall f \text{ Lipschiz,}\quad \forall y\in\mathbb S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow \int e^{-\frac{||x-y||^2}{4t}}f(x)d\mu(x)$$

@@

\vspace{0.5cm}
\begin{prop}\label{prop:2}
	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{\sqrt{n}}$, for a fixed $t>0$, a fixed Lipschitz function $f$ and a fixed point $y\in\mathbb S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
$$
\forall f \text{ Lipschitz, } \forall x\in\mathbb S^2 \quad \left|\frac{1}{4\pi t_n^2}\left(L_n^{t_n}f(x) - L^{t_n}f(x)\right)\right|\xrightarrow{n\to \infty}0.
$$
\end{prop}
\vspace{0.5cm}

@@

We define for simplicity of notation
\begin{align}
	\phi^t(x;y) &:= e^{-\frac{||x-y||^2}{4t}}\left(f(y)-f(x)\right)\\
	K^t(x,y) &:=  e^{-\frac{||x-y||^2}{4t}}
\end{align}
We start by writing the following chain of inequalities
\begin{align*}
	||L_n^tf-L^tf||_\infty &= \max _{y\in \mathbb S^2} \left|L_n^tf(y)-L^tf(y)\right|\\
	&= \max _{y\in \mathbb S^2} \left| \frac{1}{n} \sum_{i=1}^n \phi^t(x_i; y)- \int_{\mathbb S^2} \phi^t(x;y)d\mu(x) \right|\\
	&\leq \max _{y\in \mathbb S^2}  \sum_{i=1}^n   \left| \frac{1}{n}  \phi^t(x_i; y)- \int_{\sigma_i} \phi^t(x;y)d\mu(x) \right|\\
	&\leq  \max _{y\in \mathbb S^2} \left[\mathcal L_{\phi^t_y}d^{(n)} \right]\\
\end{align*}
where $\mathcal L_{\phi^t_y}$ is the Lipschitz constant of $x \rightarrow \phi^t(x, y)$ and where we used for the last inequality Proposition \ref{prop:1}. If we assume $d^{(n)}\leq \frac{C}{\sqrt{n}}$ we have that

$$||L_n^tf-L^tf||_\infty  \leq  \max _{y\in \mathbb S^2} \left[ \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]$$

@@

So we can continue
$$\begin{aligned}
	\max _{y\in \mathbb S^2} \left[  \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]
	&\leq  \frac{C}{\sqrt{n}} \left( (2et)^{-\frac{1}{2}} \norm{f}_\infty + \mathcal L_f \right)\\
	&\leq \frac{C\norm{f}_\infty}{\sqrt{n}(2et)^{1/2}} +   \frac{C}{\sqrt{n}}\mathcal L_f\\
\end{aligned}$$
So we have that, rescaling by a factor $\frac{1}{4\pi t^2}$
\begin{align*}
	\norm{\frac{1}{4\pi t^2}\left(L_n^tf-L^tf\right)}_\infty&\leq \frac{1}{4\pi t^2}\norm{\left(L_n^tf-L^tf\right)}_\infty \\
	&\leq \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{\sqrt{n}t^{5/2}} + \frac{\mathcal L_f}{\sqrt{n}t^2}\right]
\end{align*}

@@

Theorem  \ref{theo:pointwise convergence for a regular sampling}, is then an immediate consequence of Proposition \ref{prop:2} and Proposition \ref{prop:3}.
\begin{proof}[Proof of Theorem \ref{theo:pointwise convergence for a regular sampling}]
	Thanks to Proposition \ref{prop:2} and Proposition \ref{prop:3}	we conclude that $\forall y\in\mathbb S^2 $
	$$\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) =  \lim_{n\to\infty}\frac{1}{4\pi t_n^2} L^{t_n}f(y) = \frac{1}{|\mathbb S^2|}\triangle_{\mathbb S^2}f(y) $$
\end{proof}

>>>>

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
%\input{math_commands.tex}
\usepackage{amsmath,amsfonts,bm}

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{siunitx} % used in SHREC table
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
\usepackage[export]{adjustbox} % figure vertical alignment
\usepackage{subfig}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\renewcommand{\b}[1]{{\bm{#1}}}   % bold symbol
\newcommand{\bO}{\mathcal{O}}
\newcommand{\R}{\mathbb{R}}
\renewcommand{\S}{\mathbb{S}}

@@

\newcommand{\figref}[1]{figure~\ref{fig:#1}}
\newcommand{\Figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\tabref}[1]{table~\ref{tab:#1}}
\newcommand{\Tabref}[1]{Table~\ref{tab:#1}}
\newcommand{\secref}[1]{section~\ref{sec:#1}}
\newcommand{\Secref}[1]{Section~\ref{sec:#1}}
%\newcommand{\secref}[1]{\S\ref{sec:#1}}
\newcommand{\eqnref}[1]{equation~(\ref{eqn:#1})}
\newcommand{\Eqnref}[1]{Equation~(\ref{eqn:#1})}

@@

\subsection{Problem formulation}
% The plan for this section
% 0.1 Explain the sampling problem
As the graph convolution acts on a sampled version of the function $\b{f}$ and the rotation on its continuous counterpart $f$, a sampling operator is needed.
Given a sampling scheme $V=\{x_i\in\S^2, i=0, \dots, n\}$ of the sphere and a function $f : \S^2 \supset F_V \to \R$, the sampling operator $T_V: L^2(\S^2) \supset F\to \R^n,\  T_V(f) = \b{f}$ is defined as $\b{f}:\ f_i=f(x_i)$, where $F_V$ suitable subspace of $L^2(\S^2)$ such that $T_V$ is invertible, i.e., we can unambiguously reconstruct the function $f\in F_V$ from its sampled values $\b{f}$.
The existence of such subspace depends on the sampling scheme $V$, and its characterization is a common problem in signal processing (\cite{driscoll1994Fouriersphere}).
For most sampling schemes, it is not known if $F_V$ exist and hence if $T_V$ is invertible. A special case is the \textit{equiangular sampling} scheme where a sampling theorem holds, and thus we have a closed form of $T_V^{-1}$ is known. % \cite{driscoll1994Fouriersphere}
For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\bf{f}$, thus approximating $T_V^{-1}$.
For all theoretical consideration, we assume that $F_V$ exists and $f \in F_V$.

@@

\paragraph{Theoretical convergence.}
We extend the work of Belkin and Nyiogi to a sufficiently regular, deterministic sampling scheme. 
Given a sampling scheme $V = \{x_0, \dots, x_{n-1}\}$, define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\R^3$ containing $\sigma_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
\begin{theorem}
	For a sampling $V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  for $n\to\infty$:
	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} \b{L}_n^{t_n} f(x_i) =  \Delta_{\mathbb{S}^2}f(x_i)\quad \forall i=0, ..., n-1.$$
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
This theorem implies immediately that $\b{L}$ converges pointwisely toward an operator ($\Delta_{\S^2}$) commuting with rotation and hence is a strong hint for equivariance.
Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{sec: appendix: proof of theorem} inspires us in the construction of our graph Laplacian. It gives us a strong hint how the parameter $t$ needs to be adjusted with respect to the number of points $n$.

@@

\paragraph{Preliminaries.}
The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_Vf=\b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
The proof is constructed by leveraging 3 different operators:
\begin{itemize}
    \item The extended graph Laplacian operator is a functional $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
	Note that we have the following relation $\b{L}_n^t \b{f} = T_V L_n^t f$.
	\item The functional approximation to the Laplace-Beltrami operator is a functional $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
	\begin{equation}
    \label{eq:Functional approximation to the Laplace-Beltrami operator}
	L^tf(y) = \int_{\mathcal{M}} \exp^{-\frac{\|y-x\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
	\end{equation}
	where given $\mu$ be the uniform probability measure on the manifold $\mathcal{M}$, and let $\text{vol}(\mathcal{M})$ be the volume of $\mathcal{M}$.
	\item 
	The Laplace-Beltrami operator $\Delta_{\mathcal{M}}$ is defined as the divergence of the gradient
	\begin{equation}
        \label{eq:laplace-beltrami}
        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
    \end{equation}
    of a differentiable function $f: \mathcal M\rightarrow \R$. The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$

@@

% it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\S^2}f(x)$
% where $L_n^t$ is defined as follows:

@@

We start by proving the following Proposition:
\vspace{0.5cm}
\begin{prop}\label{prop:1}
	For an equal area sampling $\{x_i\in\S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $\mathcal L_f$
	$$
	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.
	$$
	Furthermore, for all $y\in\S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
	$$ L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).$$
\end{prop}
\vspace{0.5cm}

@@

	Let us assume that the function $f:\R^3\rightarrow \R$ is Lipschitz with Lipschitz constant $\mathcal L_f$, we have

@@

	So, by triangular inequality and by summing all the contributions of all the $n$ patches
	$$\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right| \leq \sum_i \left| \int_{\sigma_{i}}f({ x})\text{d}{\mu(x)} - \frac{1}{n}f( x_i)\right|\leq n  \mathcal L_fd^{(n)}\frac{1}{n} = \mathcal L_fd^{(n)}$$
	Thanks to this result, we have the following two pointwise convergences

	$$\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}\rightarrow \int e^{-\frac{||x-y||^2}{4t}}d\mu(x)$$
	$$\forall f \text{ Lipschiz,}\quad \forall y\in\S^2,  \quad\quad \frac{1}{n}\sum_i e^{-\frac{||x_i-y||^2}{4t}}f(x_i)\rightarrow \int e^{-\frac{||x-y||^2}{4t}}f(x)d\mu(x)$$

@@

\vspace{0.5cm}
\begin{prop}\label{prop:2}
	Given a sampling regular enough, i.e., for which we assume $A_i=A_j \ \forall i,j\text{ and }d^{(n)}\leq \frac{C}{\sqrt{n}}$, for a fixed $t>0$, a fixed Lipschitz function $f$ and a fixed point $y\in\S^2$ there exists a sequence $t_n = n^\beta, \beta<0$ such that
$$
\forall f \text{ Lipschitz, } \forall x\in\S^2 \quad \left|\frac{1}{4\pi t_n^2}\left(L_n^{t_n}f(x) - L^{t_n}f(x)\right)\right|\xrightarrow{n\to \infty}0.
$$
\end{prop}
\vspace{0.5cm}

@@

We define for simplicity of notation
\begin{align}
	\phi^t(x;y) &:= e^{-\frac{||x-y||^2}{4t}}\left(f(y)-f(x)\right)\\
	K^t(x,y) &:=  e^{-\frac{||x-y||^2}{4t}}
\end{align}
We start by writing the following chain of inequalities
\begin{align*}
	||L_n^tf-L^tf||_\infty &= \max _{y\in \S^2} \left|L_n^tf(y)-L^tf(y)\right|\\
	&= \max _{y\in \S^2} \left| \frac{1}{n} \sum_{i=1}^n \phi^t(x_i; y)- \int_{\S^2} \phi^t(x;y)d\mu(x) \right|\\
	&\leq \max _{y\in \S^2}  \sum_{i=1}^n   \left| \frac{1}{n}  \phi^t(x_i; y)- \int_{\sigma_i} \phi^t(x;y)d\mu(x) \right|\\
	&\leq  \max _{y\in \S^2} \left[\mathcal L_{\phi^t_y}d^{(n)} \right]\\
\end{align*}
where $\mathcal L_{\phi^t_y}$ is the Lipschitz constant of $x \rightarrow \phi^t(x, y)$ and where we used for the last inequality Proposition \ref{prop:1}. If we assume $d^{(n)}\leq \frac{C}{\sqrt{n}}$ we have that

$$||L_n^tf-L^tf||_\infty  \leq  \max _{y\in \S^2} \left[ \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]$$

@@

So we can continue
$$\begin{aligned}
	\max _{y\in \S^2} \left[  \mathcal L_{\phi^t_y} \frac{C}{\sqrt{n}} \right]
	&\leq  \frac{C}{\sqrt{n}} \left( (2et)^{-\frac{1}{2}} \norm{f}_\infty + \mathcal L_f \right)\\
	&\leq \frac{C\norm{f}_\infty}{\sqrt{n}(2et)^{1/2}} +   \frac{C}{\sqrt{n}}\mathcal L_f\\
\end{aligned}$$
So we have that, rescaling by a factor $\frac{1}{4\pi t^2}$
\begin{align*}
	\norm{\frac{1}{4\pi t^2}\left(L_n^tf-L^tf\right)}_\infty&\leq \frac{1}{4\pi t^2}\norm{\left(L_n^tf-L^tf\right)}_\infty \\
	&\leq \frac{C}{4\pi}\left[\frac{\norm{f}_\infty}{\sqrt{2e}}\frac{1}{\sqrt{n}t^{5/2}} + \frac{\mathcal L_f}{\sqrt{n}t^2}\right]
\end{align*}

@@

Theorem  \ref{theo:pointwise convergence for a regular sampling}, is then an immediate consequence of Proposition \ref{prop:2} and Proposition \ref{prop:3}.
\begin{proof}[Proof of Theorem \ref{theo:pointwise convergence for a regular sampling}]
	Thanks to Proposition \ref{prop:2} and Proposition \ref{prop:3}	we conclude that $\forall y\in\S^2 $
	$$\lim_{n\to\infty}\frac{1}{4\pi t_n^2} L_n^{t_n}f(y) =  \lim_{n\to\infty}\frac{1}{4\pi t_n^2} L^{t_n}f(y) = \frac{1}{|\S^2|}\triangle_{\S^2}f(y) $$
\end{proof}
